%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape LAKSHAY} \\ \vspace{1pt}
    \small +91-8814020280 $|$ \href{mailto:lakshaygarg9812@gmail.com}{\underline{lakshaygarg9812@gmail.com}} $|$
    \href{https://www.linkedin.com/in/igarglakshay}{\underline{linkedin.com/in/igarglakshay}} $|$
    \href{https://github.com/lakshaygarg755}{\underline{github.com/lakshaygarg755}} $|$
    \href{https://lakshaygarg.is-a.dev}{\underline{lakshaygarg.is-a.dev}}
\end{center}


%-----------OBJECTIVE-----------
\section{Objective}
  \small{Aspiring \textbf{Software Development Engineer (SDE)} with a focus on \textbf{Full Stack} and \textbf{Backend Development}. Passionate about building interactive user experiences.}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology, Manipur}{Manipur, India}
      {Bachelor of Technology in Computer Science and Engineering; CGPA: 7.46}{2022 -- 2026}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Full-Stack Developer Intern}{Remote}
      {Satvify}{Jan 2026 -- May 2026}
      \resumeItemListStart
        \resumeItem{Engineered a comprehensive e-commerce platform using \textbf{React.js, Node.js, Express.js, and PostgreSQL}, delivering a seamless shopping experience for healthy and vegan products.}
        \resumeItem{Integrated \textbf{Razorpay} for secure payment processing and deployed the scalable architecture on \textbf{AWS}.}
        % \resumeItem{Architected system design, including Data Flow Diagrams (DFDs) and Entity-Relationship (ER) models for robust data management.}
      \resumeItemListEnd

    \resumeSubheading
      {Intern Developer}{Remote}
      {MBSGames}{May 2025 -- July 2025}
      \resumeItemListStart
        \resumeItem{Developed core gameplay mechanics for 'Tiny Toads,' an educational mobile game, utilizing \textbf{Unity and C\#} to enhance user engagement and learning outcomes.}
        \resumeItem{Engineered interactive learning modules (alphabet drawing, number counting) and optimized performance, resulting in a smoother user experience on low-end devices.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/lakshaygarg755/course_organizer}{Course Directory}} | \href{https://course-organizer.onrender.com/}{\underline{Live Demo}} | \emph{Express.js, ejs, Node.js, MongoDB}}{Jan 2025 -- Feb 2025}
          \resumeItemListStart
            \resumeItem{Architected a full-stack educational platform using Node.js, Express.js, and MongoDB (Mongoose) with an EJS and Bootstrap 5 frontend to centralize university course management.}
            \resumeItem{Implemented secure user authentication and Role-Based Access Control using Passport.js and bcrypt, enabling admins to manage curriculum while students access materials.}
            \resumeItem{Integrated Cloudinary cloud storage via Multer to securely process and host permanent uploads of lecture PDFs and assignment files, optimizing server storage.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{\href{https://github.com/lakshaygarg755/chatapp}{Real-Time Chat Application}} $|$ \emph{Node.js, Express.js, Socket.io}}{2025}
          \resumeItemListStart
            \resumeItem{Real-time chat application supporting multiple users and private messaging.}
            \resumeItem{Integrated WebSockets for real-time communication and authentication for secure login.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{\href{https://github.com/lakshaygarg755/Algo-visualiser}{Network Scheduling Algorithm Visualizer}} $|$ \emph{C++, Qt Framework}}{Aug 2024 -- Oct 2024}
          \resumeItemListStart
            \resumeItem{Designed and implemented an interactive visualization tool for 5 network scheduling algorithms.}
            \resumeItem{Enabled real-time simulation where users can input the number of packets, time sequences, and output flow rate, dynamically visualizing the algorithm's behavior.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: C/C++, JavaScript} \\
      \textbf{Frameworks \& Libraries}{: Node.js, Express.js, Bootstrap, Tailwind CSS} \\
      \textbf{Databases}{: MySQL, PostgreSQL, SQL/NoSQL Design} \\
      \textbf{Developer Tools}{: Git, GitHub, VS Code, npm, Postman} \\
      \textbf{Cloud \& Deployment}{: Render} \\
    }}
 \end{itemize}

 
%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Core CS}{: Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems, Computer Networks, Database Management Systems, Compiler Design} \\
     \textbf{AI \& ML}{: Artificial Intelligence, Machine Learning, Natural Language Processing, Information Retrieval} \\
     \textbf{Systems \& Security}{: Cloud Computing, Cyber Security, Cryptography, Internet of Things (IoT)} \\
    }}
 \end{itemize}


%-----------CERTIFICATIONS & LEADERSHIP-----------
\section{Certifications \& Leadership}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Web Development Bootcamp} - Udemy (Mar 2024) | 65-hour full-stack development training. \\
      \textbf{Team Lead - Smart India Hackathon 2024} (Aug 2024) | Led 6-person development team using Agile/Scrum. \\
      \textbf{Problem Solving} | Solved 500+ coding problems on \href{https://www.hackerrank.com/profile/lakshaygarg9812}{HackerRank} and \href{https://leetcode.com/u/iiitm_042301/}{LeetCode}. \\
      \textbf{Ethical Hacking and Penetration Testing} - C-DAC NOIDA (Dec 2024 -- Jan 2025) | Completed online training \& virtual internship under Cyber Gyan Project.
    }}
 \end{itemize}

\end{document}